Regular singular Volterra equations on complex domains

### 2024-07-29 sima/reg-sing-volterra_sima.tex
Commit before dropping old text
Use explicit moving point instead of dot in some integrals

% drafting environments
\newenvironment{brainstorm}{\color{violet}\begin{itemize}}{\end{itemize}\color{black}}

@@

% revision highlighting
\newif\ifhighlightrevs
\highlightrevstrue
\ifhighlightrevs
\newenvironment{rev}{\color{revred}}{\color{black}}
\newcommand{\revtext}[1]{\textcolor{revred}{#1}}
\else
\newenvironment{rev}{}{}
\newcommand{\revtext}[1]{#1}
\fi

@@

In its most basic form, the Laplace transform $\laplace$ turns exponential-type functions of a real ``position'' variable $\zeta$ into holomorphic functions of a complex ``frequency'' variable $z$. \begin{verify}[Suppose the magnitude of the Laplace transform integrand is Riemann-integrable on $(0, \infty)$. Write $z$ in terms of its real and imaginary parts as $x + iy$. Since the integrand is holomorphic with respect to $z$, the operator $\frac{\partial}{\partial\overline{z}} = \frac{1}{2}\left(\frac{\partial}{\partial x} + i\frac{\partial}{\partial x}\right)$ annihilates it. Using the comparison version of Leibniz's rule for improper integrals (Theorem~11.10 of A First Course in Real Analysis, by Protter and Morrey) with $\frac{\partial}{\partial x}$ and $\frac{\partial}{\partial y}$, we see that $\frac{\partial}{\partial\overline{z}}$ annihilates the whole integral.]\end{verify} Through identities like
\begin{align*}
\frac{\partial}{\partial z} \laplace \varphi & = \laplace(-\zeta\varphi) \\
\laplace k\;\laplace \varphi & = \laplace(k * \varphi) \\
z^{-\nu} \laplace \varphi & = \laplace\,\partial^{-\nu} \varphi,
\end{align*}
where $\partial^{-\nu}$ is the Riemann-Liouville fractional integral of order $\nu \in (0, \infty)$, the Laplace transform pulls differential operators on the frequency domain back to Volterra integral operators on the position domain. The favorable regularity properties and comprehensive theory of Volterra equations can thus be brought to bear on linear differential equations.

Some differential equations pull back to Volterra equations with real-analytic kernels, which extend to holomorphic Volterra equations on complex extensions of the position domain. \begin{rev}For instance, in Section~\ref{sec:example}, we consider equations of the form
\begin{equation}\label{eqn:intro-level-1}
\left[ P\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z} Q\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z^2} R(z^{-1}) \right] \Phi = 0
\end{equation}
given by polynomials $P$, $Q$ and a holomorphic function $R(z^{-1})$ satisfying some extra conditions. A function of the form $\Phi = \laplace \varphi$ satisfies this equation if and only if $\varphi$ satisfies the integral equation
\begin{equation}\label{eqn:intro-use-dict}
\big[ P(-\zeta)+\partial^{-1}\circ Q(-\zeta)+\partial^{-2}\circ R(\partial^{-1}) \big] \varphi = 0.
\end{equation}
The integral operator remains well-defined if we make $\zeta$ a complex coordinate and seek solutions $\varphi$ which extend holomorphically into the complex position domain.

Equation~\eqref{eqn:intro-level-1} can be solved by resumming normal series, as described earlier. Each resummed solution is characterized by its $e^{-\alpha z} z^{-\tau_\alpha}$ asymptotics, where $-\alpha$ is a root of $P$ and $\tau_\alpha = Q(-\alpha)/P'(-\alpha)$ is real and positive. To obtain this solution analytically through Laplace transform methods, we must take the Laplace transform $\laplace_{\zeta,\alpha}$ that uses $\zeta = \alpha$ in place of the traditional $\zeta = 0$ as the integration base point. Equation~\eqref{eqn:intro-use-dict} then comes out based at $\zeta = \alpha$ as well. We seek a solution $\psi_\alpha$ which
\begin{itemize}
\item has an $O\big((\zeta - \alpha)^{\tau_\alpha-1}\big)$ singularity at $\zeta = \alpha$; and
\item is of exponential type, meaning that it is $O\big(e^{\Lambda|\zeta|}\big)$ for some $\Lambda \in \R$ as $\zeta$ grows.
\end{itemize}
These conditions ensure that $\psi_\alpha$ has a well-defined Laplace transform, and the first condition gives $\laplace_{\zeta, \alpha} \psi_\alpha$ the desired asymptotics.

@@

For simplicity, we use $\C$ as the position domain throughout this article. In the study of resurgence, however, the position domain is often a Riemann surface over $\C$, or even a more general ``translation surface.'' Thanks to our choice of formalism, our results and their proofs generalize immediately to this setting.
\subsubsection{Points and coordinates}
From now on, we will carefully respect the distinction between points and coordinates. A point is a location in space, while a coordinate is a function on space. For example, the position coordinates $\zeta$ and $\zeta_\alpha$ are functions on the position domain, just like the integral equation solutions $\psi_\alpha$. A coordinate, like $\zeta$, can be evaluated at a point $b$, yielding a number $\beta := \zeta(b)$. Conversely, the point $b$ can be described as the place where $\zeta = \beta$.
\subsubsection{Integration}
When we integrate, the integrand will always be either a 1-form, like $\varphi\,d\zeta$, or a density, like $|\varphi\,d\zeta|$~\cite[Section~1.8]{local-viewpoint}. On a simply connected domain, all integration paths are equivalent, so we will typically specify an integral by its start and end points. These points may be given directly, as in the expression $\int_b^a \varphi\,d\zeta$, or described in terms of coordinates, as in the equivalent expression $\int_{\zeta = \beta}^a \varphi\,d\zeta$. In the integral
\[ \int_{\zeta = \beta}^a \big(\zeta(a) - \zeta\big)^{-1/2} \varphi\,d\zeta, \]
notice that $\zeta(a)$ is a number, which stays constant throughout the integration, while $\zeta$ is a function, whose value changes along the integration path.
\subsubsection{Plugging into formal expressions}
Plugging a function $\varphi$ into a formal polynomial or power series $P$ gives a new function $P(\varphi)$. The correspondence between operators on the position and frequency domains will lead to expressions of this kind. In Section~\ref{sec:motivation}, for example, we saw that the differential operator $P\big(\tfrac{\partial}{\partial z}\big)$ on the frequency domain corresponds to multiplication by the function $P(-\zeta)$ on the position domain.\end{rev}
\subsection{Notation}
\subsubsection{Uniform bounds}
Given a complex-valued function $\varphi$ and a non-negative, real-valued function $\omega$, we will write \revtext{$|\varphi| \lesssim \omega$} to say that $|\varphi|$ is bounded by a constant multiple of $\omega$. Unless we say otherwise, the bound holds throughout the domain where both functions are defined. If the bound invovles an explicit variable, we will say that it holds over all values of the variable. For example, we will write ``$|R_j| \lesssim \lambda^j$ over all $j \in \{0, 1, 2, \ldots\}$'' to mean ``there is a constant $M$ such that for all $j \in \{0, 1, 2, \ldots\}$, the inequality $|R_j| \le M \lambda^j$ holds.''
\begin{rev}\subsubsection{Boundary points}
We will say that a subset of a topological space {\em touches} the points in its closure. This is a way of expressing the nearness relation associated with the topology~\cite[Chapter~5, Definition~2.11]{joshi1983gen-top}. If $\Omega \subset \C$ touches the $p \in \C$, we define a neighborhood of $p$ in $\Omega$ to be $U \cap \Omega$ for some open neighboorhood $U \subset \C$ of $p$. This agrees with the usual definition of a neighborhood when $p$ is an element of $\Omega$.\end{rev}
\subsection{Setting}\label{setting}
\subsubsection{The domain}\label{setting:domain}
Throughout this paper, as described in Section~\ref{sec:motivation}, the position variable $\zeta$ will be the standard coordinate on $\C$.

@@

Let $\holo(\domain)$ be the space of holomorphic functions on $\domain$.
\begin{definition}\label{defn:volterra}
A {\em holomorphic Volterra operator} on $\domain$ is a linear operator
\[\genvolterra\colon\holo(\domain)\to\holo(\domain) \]
defined by an integral
\[ [\genvolterra\,\varphi](a) = \int_{\zeta = 0}^a \genker(a, \cdot)\,\varphi\;d\zeta \]
in which the {\em kernel} $w$ is a holomorphic function on $\Omega^2$.
\end{definition}
\begin{definition}
A holomorphic Volterra operator is {\em separable} if its kernel factors as a product of two functions, one on each factor of $\Omega^2$.
\end{definition}
For the prototype operator $\hardpart$, we will suppose that the kernel $\hardker$ can be written as a ratio
\[ \hardker(a, a') = - \frac{q(a')}{p(a)}, \]
for some $p, q \in \mathcal{H}(\Omega)$.\end{rev}

@@

We now perturb $\hardpart$ to a more general operator $\volterra=\hardpart +\softpart$. \revtext{The perturbation $\softpart$ will be non-separable,}\footnote{Unless $\softpart$ is zero, of course.} but it will have a regularizing effect, as we will show in Proposition \ref{prop:smoothing}. To get the smoothing effect, we will require the kernel $\softker$ of $\softpart$ to vanish to some order $\gamma > 0$ on the diagonal in $\domain^2$. This requirement, combined with two others, will be made precise in Condition~\eqref{cond:eps-lambda}.

@@

\subsection{Main results}\label{sec:results}
We want to show that when $\volterra$ is a regular singular Volterra operator of the kind described in Section~\ref{setting:perturbed}, the equation $f = \volterra f$ has a unique solution of a certain form. For the prototypical operator $\hardpart$ described in Section~\ref{setting:basic}, this solution can be written explicitly.
\begin{theorem}\label{thm:basic_volterra}
Suppose $\hardpart$ satisfies {\em Condition \eqref{cond:sing}}. Then the equation
\begin{equation}\label{eq:hardpart}
f = \hardpart f    
\end{equation}
has the {\em prototype solution}
\begin{equation}\label{eqn:test_solution}
\solproto(a) = \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
\end{equation}
Changing the base point $b \in \domain$ \revtext{only} multiplies $f_0$ by a non-zero constant.
\end{theorem}
We will prove this result in Section~\ref{sec:construction}.

The solution $\solproto$ from Theorem~\ref{thm:basic_volterra} has, at worst, a mild power-law singularity at $\zeta = 0$. \revtext{When $\hardpart$ is especially regular, $\solproto$ also grows at most exponentially as $|\zeta| \to \infty$.} The function spaces defined in Section~\ref{fn-spaces} express both of these regularity properties.
\begin{theorem}\label{thm:proto-growth}
Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:sing}}. Then, on a small enough neighborhood of $\zeta = 0$, we have $|\solproto| \lesssim |\zeta|^{\tau-1}$.

@@

\revtext{The perturbed equation $f = \volterra f$ is more complicated, but its regular singularity at $\zeta = 0$ is essentially the same.} We might therefore \revtext{expect a solution} that looks like $\solproto$ near the singularity, differing only by a less singular perturbation. If we strengthen the constraints on $\hardpart$ a little more, this expectation is fulfilled.
\begin{theorem}\label{thm:general_volterra}
Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition~\eqref{cond:eps-lambda}}. Then the equation
\[ f = \volterra f \]
has a unique solution $f$ in the affine subspace
\[ f_0 + \singexpalg{\tau-1+\gamma}(\Omega) \]
of the space $\singexpalg{\tau-1}(\Omega)$ defined in Section~\ref{fn-spaces}. Here, $f_0$ is the prototype solution \eqref{eqn:test_solution} from Theorems \ref{thm:basic_volterra}--\ref{thm:proto-growth}, which belongs to the space $\singexpalg{\tau-1}(\domain)$.
\end{theorem}
\begin{rev}\begin{corollary}\label{cor:expand_uniq}
Under the conditions of Theorem~\ref{thm:general_volterra}, for any $\rho > \tau$, the equation $f = \volterra f$ has at most one solution in $f_0 + \singexpalg{\rho-1}(\Omega)$. 
\end{corollary}\end{rev}
This result will follow from a more general result about inhomogeneous equations.
\begin{lemma}\label{lem:perturbed_volterra}
Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}. Suppose we are also given a function $g$, which for some $\rho > \tau$ belongs to the space $\singexpalg{\rho-1}(\Omega)$ defined in Section~\ref{fn-spaces}. Then the inhomogeneous equation
\[ f = \volterra f + g, \]
has a unique solution $f$ in the space $\singexpalg{\rho-1}(\Omega)$.
\end{lemma}
We will prove Lemma~\ref{lem:perturbed_volterra} in Sections \ref{sec:V is a contraction}--\ref{sec:existence and uniqueness}, using the contraction mapping theorem. The heart of the argument is Proposition~\ref{prop:get-contraction}, which shows us how to find relevant subspaces where $\volterra$ is a contraction.

@@

\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_0^a |k(a, \cdot)\,\varphi\;d\zeta| \]

@@

@@

|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_0^a |k(a, \cdot)|\,|\zeta|^{\rho-1}\,e^{\Lambda |\zeta|}\,\|\varphi\|_{\rho-1, \Lambda}\;|d\zeta| \\
& = \|\varphi\|_{\rho-1, \Lambda}  \int_0^a |k(a, \cdot)|\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|

@@

@@

\|\varphi\|_{\rho-1, \Lambda}  \int_0^a \frac{\sigma}{|\zeta(a)|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta| \\
& \le \sigma \|\varphi\|_{\rho-1, \Lambda}  \int_0^a \left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;\left|\frac{d\zeta}{\zeta(a)}\right|

>>>>

% drafting environments
\newenvironment{brainstorm}{\color{violet}\begin{itemize}}{\end{itemize}\color{black}}
\newenvironment{todo}{\color{violet}}{\color{black}}

@@

% revision highlighting
\newif\ifhighlightrevs
\highlightrevstrue 
\ifhighlightrevs
\newenvironment{rev}{\color{ietocean}}{\color{black}}
\newcommand{\revtext}[1]{\textcolor{ietocean}{#1}}
\newenvironment{revtwo}{\color{revred}}{\color{black}}
\newcommand{\revtwotext}[1]{\textcolor{revred}{#1}}
\else
\newenvironment{rev}{}{}
\newcommand{\revtext}[1]{#1}
\newenvironment{revtwo}{}{}
\newcommand{\revtwotext}[1]{#1}
\fi

% notation change highlighting
\newif\ifhighlightnewnotation
\highlightnewnotationtrue
\ifhighlightnewnotation
\newenvironment{newnot}{\color{orange}}{\color{black}}
\newcommand{\newnottext}[1]{\textcolor{orange}{#1}}
\newenvironment{oldnot}{\color{cyan}}{\color{black}}
\newcommand{\oldnottext}[1]{\textcolor{cyan}{#1}}
\else
\newenvironment{newnot}{}{}
\newenvironment{oldnot}{}{}
\newcommand{\newnottext}[1]{#1}
\fi

@@

In its most basic form, the Laplace transform $\laplace$ turns exponential-type functions of a real ``position'' variable $\zeta$ into holomorphic functions of a complex ``frequency'' variable $z$. It is the integral transform defined by the equation
\[ \laplace \varphi := \int_{\Gamma_\zeta} e^{-z\zeta} \varphi\;d\zeta\,, \]
where $\Gamma_\zeta$ is the ray $\zeta \in (0, \infty)$. \begin{verify}[Suppose the magnitude of the Laplace transform integrand is Riemann-integrable on $(0, \infty)$. Write $z$ in terms of its real and imaginary parts as $x + iy$. Since the integrand is holomorphic with respect to $z$, the operator $\frac{\partial}{\partial\overline{z}} = \frac{1}{2}\left(\frac{\partial}{\partial x} + i\frac{\partial}{\partial x}\right)$ annihilates it. Using the comparison version of Leibniz's rule for improper integrals (Theorem~11.10 of A First Course in Real Analysis, by Protter and Morrey) with $\frac{\partial}{\partial x}$ and $\frac{\partial}{\partial y}$, we see that $\frac{\partial}{\partial\overline{z}}$ annihilates the whole integral.]\end{verify} Through identities like
\begin{align*}
\frac{\partial}{\partial z} \laplace \varphi & = \laplace(-\zeta\varphi) \\
\laplace \psi\;\laplace\varphi & = \laplace(\psi * \varphi) \\
z^{-\nu} \laplace \varphi & = \laplace\,\partial^{-\nu} \varphi\,,
\end{align*}
where $\partial^{-\nu}$ is the Riemann-Liouville fractional integral of order $\nu \in (0, \infty)$, the Laplace transform pulls differential operators on the frequency domain back to Volterra integral operators on the position domain. The favorable regularity properties and comprehensive theory of Volterra equations can thus be brought to bear on linear differential equations.

Some differential equations pull back to Volterra equations with real-analytic kernels, which extend to holomorphic Volterra equations on complex extensions of the position domain. \begin{rev}For instance, in Section~\ref{sec:example}, we consider equations of the form
\begin{equation}\label{eqn:intro-level-1}
\left[ P\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z} Q\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z^2} R(z^{-1}) \right] \Phi = 0
\end{equation}
given by polynomials $P$, $Q$ and a holomorphic function $R(z^{-1})$ satisfying some extra conditions. A function of the form $\Phi = \laplace \varphi$ satisfies this equation if and only if $\varphi$ satisfies the integral equation
\begin{equation}\label{eqn:intro-use-dict}
\big[ P(-\zeta)+\partial^{-1}\circ Q(-\zeta)+\partial^{-2}\circ R(\partial^{-1}) \big] \varphi = 0\,.
\end{equation}
The integral operator remains well-defined if we make $\zeta$ a complex coordinate and seek solutions $\varphi$ which extend holomorphically into the complex position domain.

Equation~\eqref{eqn:intro-level-1} can be solved by resumming normal series, as described earlier. Each resummed solution is characterized by its $e^{-\alpha z} z^{-\tau_\alpha}$ asymptotics, where $-\alpha$ is a root of $P$ and $\tau_\alpha = Q(-\alpha)/P'(-\alpha)$ is real and positive. To obtain this solution analytically through Laplace transform methods, we must take the Laplace transform $\laplace_{\zeta,\alpha}$ that uses $\zeta = \alpha$ in place of the traditional $\zeta = 0$ as the integration base point. This version of the Laplace transform is defined in Section~\ref{sec:definition_Laplace}. A function of the form $\Phi = \laplace_{\zeta, \alpha} \varphi$ satisfies equation~\eqref{eqn:intro-level-1} if and only if $\varphi$ satisfies the integral equation
%%use the Laplace transform based at $\zeta = \alpha$, equation~\eqref{eqn:intro-use-dict} then comes out based at $\zeta = \alpha$ as well:
\[ \big[ P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ R(\partial_{\zeta,\alpha}^{-1}) \big] \varphi = 0\,, \]
where $\partial^{-1}_{\zeta, \alpha}$ is integration with base point $\zeta = \alpha$:
\[ [\partial^{-1}_{\zeta, \alpha} \varphi](a) := \int_{\zeta = \alpha}^a \varphi\;d\zeta\,. \]
We seek a solution $\psi_\alpha$ which
\begin{itemize}
\item has an $O\big((\zeta - \alpha)^{\tau_\alpha-1}\big)$ singularity at $\zeta = \alpha$; and
\item is of exponential type, meaning that it is $O\big(e^{\Lambda|\zeta|}\big)$ for some $\Lambda \in \R$ as $\zeta$ grows.
\end{itemize}
These conditions ensure that $\psi_\alpha$ has a well-defined Laplace transform, and the first condition gives $\laplace_{\zeta, \alpha} \psi_\alpha$ the desired asymptotics.

@@

For simplicity, we use $\C$ as the position domain throughout this article. In the study of resurgence, however, the position domain is often a Riemann surface over $\C$, or even a more general ``translation surface.'' Thanks to our choice of formalism, our results and their proofs generalize immediately to this setting.
\subsubsection{Points and coordinates}
From now on, we will carefully respect the distinction between points and coordinates. A point is a location in space, while a coordinate is a function on space. For example, the position coordinates $\zeta$ and $\zeta_\alpha$ are functions on the position domain, just like the integral equation solutions $\psi_\alpha$. A coordinate, like $\zeta$, can be evaluated at a point $b$, yielding a number $\beta := \zeta(b)$. Conversely, the point $b$ can be described as the place where $\zeta = \beta$.
\subsubsection{Integration}
When we integrate, the integrand will always be either a 1-form, like $\varphi\,d\zeta$, or a density, like $|\varphi\,d\zeta|$~\cite[Section~1.8]{local-viewpoint}. On a simply connected domain, all integration paths are equivalent, so we will typically specify an integral by its start and end points. These points may be given directly, as in the expression $\int_b^a \varphi\,d\zeta$, or described in terms of coordinates, as in the equivalent expression $\int_{\zeta = \beta}^a \varphi\,d\zeta$. In the integral
\[ \int_{\zeta = \beta}^a \big(\zeta(a) - \zeta\big)^{-1/2} \varphi\,d\zeta\,, \]
notice that $\zeta(a)$ is a number, which stays constant throughout the integration, while $\zeta$ is a function, whose value changes along the integration path.

\begin{revtwo}
Sometimes, in expressions like
\[ \int_{\zeta(a') = \beta}^a w(a, a')\,\varphi(a')\,d\zeta(a')\,, \]
it is useful to give a name $a'$ to the point moving along the integration path. In this case, all of the functions and differential forms whose values change along the integration path are explicitly evaluated at $a'$.
\end{revtwo}
\subsubsection{Plugging into formal expressions}
Plugging a function $\varphi$ into a formal polynomial or power series $P$ gives a new function $P(\varphi)$. The correspondence between operators on the position and frequency domains will lead to expressions of this kind. In Section~\ref{sec:motivation}, for example, we saw that the differential operator $P\big(\tfrac{\partial}{\partial z}\big)$ on the frequency domain corresponds to multiplication by the function $P(-\zeta)$ on the position domain.\end{rev}
\subsection{Notation}
\subsubsection{Uniform bounds}
Given a complex-valued function $\varphi$ and a non-negative, real-valued function $\omega$, we will write \revtext{$|\varphi| \lesssim \omega$} to say that $|\varphi|$ is bounded by a constant multiple of $\omega$. Unless we say otherwise, the bound holds throughout the domain where both functions are defined. If the bound invovles an explicit variable, we will say that it holds over all values of the variable. For example, we will write ``$|R_j| \lesssim \lambda^j$ over all $j \in \{0, 1, 2, \ldots\}$'' to mean ``there is a constant $M$ such that for all $j \in \{0, 1, 2, \ldots\}$, the inequality $|R_j| \le M \lambda^j$ holds.''
\begin{rev}\subsubsection{Boundary points}
We will say that a subset of a topological space {\em touches} the points in its closure. This is a way of expressing the nearness relation associated with the topology~\cite[Chapter~5, Definition~2.11]{joshi1983gen-top}. If $\Omega \subset \C$ touches the $p \in \C$, we define a neighborhood of $p$ in $\Omega$ to be $U \cap \Omega$ for some open neighboorhood $U \subset \C$ of $p$. This agrees with the usual definition of a neighborhood when $p$ is an element of $\Omega$.\end{rev}
\subsection{Setting}\label{setting}
\subsubsection{The domain}\label{setting:domain}
Throughout this paper, as described in Section~\ref{sec:motivation}, the position variable $\zeta$ will be the standard coordinate on $\C$.

@@

Let $\holo(\domain)$ be the space of holomorphic functions on $\domain$.
\begin{definition}\label{defn:volterra}
A {\em holomorphic Volterra operator} on $\domain$ is a linear operator
\[\genvolterra\colon\holo(\domain)\to\holo(\domain) \]
defined by an integral
\begin{oldnot}
\[ [\genvolterra\,\varphi](a) = \int_{\zeta = 0}^a \genker(a, \cdot)\,\varphi\;d\zeta \]
\end{oldnot}
\begin{newnot}\begin{todo}[Possibility: use moving point to write kernel with both arguments]\end{todo}
\[ [\genvolterra\,\varphi](a) = \int_{\zeta(a') = 0}^a \genker(a, a')\,\varphi(a')\;d\zeta(a') \]
\end{newnot}
\begin{newnot}\begin{todo}[Possibility: ``integration along $\zeta''$ with $\zeta'$ fixed]\end{todo}
\[ \genvolterra\,\varphi = \int_{0}^{\zeta} \genker\,\varphi''\;d\zeta''\Big|_{\zeta' = \zeta} \]
\end{newnot}
in which the {\em kernel} $w$ is a holomorphic function on $\Omega^2$.
\end{definition}
\begin{definition}
A holomorphic Volterra operator is {\em separable} if its kernel factors as a product of two functions, one on each factor of $\Omega^2$.
\end{definition}
For the prototype operator $\hardpart$, we will suppose that the kernel $\hardker$ can be written as a ratio
\[ \hardker(a, a') = - \frac{q(a')}{p(a)}, \]
for some $p, q \in \mathcal{H}(\Omega)$. \end{rev}\begin{revtwo}Explicitly,
\[ \big[\hardpart \varphi\big](a) = - \int_{\zeta=0}^{a} \frac{q}{p(a)}\,\varphi\;d\zeta\,. \]
\end{revtwo}

@@

We now perturb $\hardpart$ to a more general operator $\volterra = \hardpart +\softpart$. \begin{revtwo}The perturbation
\begin{oldnot}
\[ [\softpart\,\varphi](a) := \int_{\zeta = 0}^a \softker(a, \cdot)\,\varphi\;d\zeta \]
\end{oldnot}
\begin{newnot}
\[ [\softpart\,\varphi](a) := \int_{\zeta(a') = 0}^a \softker(a, a')\,\varphi(a')\;d\zeta(a') \]
\end{newnot}
will be non-separable,\end{revtwo}\footnote{Unless $\softpart$ is zero, of course.} but it will have a regularizing effect, as we will show in Proposition \ref{prop:smoothing}. To get the smoothing effect, we will require \revtwotext{the kernel $\softker$} to vanish to some order $\gamma > 0$ on the diagonal in $\domain^2$. This requirement, combined with two others, will be made precise in Condition~\eqref{cond:eps-lambda}.

@@

\subsection{Main results}\label{sec:results}
We want to show that when $\volterra$ is a regular singular Volterra operator of the kind described in Section~\ref{setting:perturbed}, the equation $f = \volterra f$ has a unique solution of a certain form. For the prototypical operator $\hardpart$ described in Section~\ref{setting:basic}, this solution can be written explicitly.
\begin{theorem}\label{thm:basic_volterra}
\begin{revtwo}Suppose the operator%%$\hardpart$
\[ \big[\hardpart \varphi\big](a) := - \int_{\zeta=0}^{a} \frac{q}{p(a)}\,\varphi\;d\zeta \]
\end{revtwo}
satisfies {\em Condition \eqref{cond:sing}}. Then the equation
\begin{equation}\label{eq:hardpart}
f = \hardpart f    
\end{equation}
has the {\em prototype solution}
\begin{equation}\label{eqn:test_solution}
\solproto(a) = \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
\end{equation}
Changing the base point $b \in \domain$ \revtext{only} multiplies $f_0$ by a non-zero constant.
\end{theorem}
We will prove this result in Section~\ref{sec:construction}.

The solution $\solproto$ from Theorem~\ref{thm:basic_volterra} has, at worst, a mild power-law singularity at $\zeta = 0$. \revtext{When $\hardpart$ is especially regular, $\solproto$ also grows at most exponentially as $|\zeta| \to \infty$.} The function spaces defined in Section~\ref{fn-spaces} express both of these regularity properties. \begin{revtwo}We will state our results in terms of the spaces $\singexpalg{\sigma}(\domain)$, which are defined as unions of normed spaces. Every function $f \in \singexpalg{\sigma}(\domain)$ has a finite norm
\[ \|f\|_{\sigma,\Lambda} := \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f| \]
for some $\Lambda \in \R$.
\end{revtwo}
\begin{theorem}\label{thm:proto-growth}
\begin{revtwo}Suppose the operator%%$\hardpart$
\[ \big[\hardpart \varphi\big](a) := - \int_{\zeta=0}^{a} \frac{q}{p(a)}\,\varphi\;d\zeta \]
\end{revtwo}
satisfies {\em Condition~\eqref{cond:sing}}. Then, on a small enough neighborhood of $\zeta = 0$, we have $|\solproto| \lesssim |\zeta|^{\tau-1}$.

@@

\revtext{The perturbed equation $f = \volterra f$ is more complicated, but its regular singularity at $\zeta = 0$ is essentially the same.} We might therefore \revtext{expect a solution} that looks like $\solproto$ near the singularity, differing only by a less singular perturbation. If we strengthen the constraints on $\hardpart$ a little more, this expectation is fulfilled.
\begin{theorem}\label{thm:general_volterra}
Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and \begin{revtwo}the perturbation
\begin{oldnot}
\[ [\softpart\,\varphi](a) := \int_{\zeta = 0}^a \softker(a, \cdot)\,\varphi\;d\zeta \]
\end{oldnot}
\begin{newnot}
\[ [\softpart\,\varphi](a) := \int_{\zeta(a') = 0}^a \softker(a, a')\,\varphi(a')\;d\zeta(a') \]
\end{newnot}
\end{revtwo}
satisfies {\em Condition~\eqref{cond:eps-lambda}}. Then the equation
\[ f = \volterra f \]
has a unique solution $f$ in the affine subspace
\[ f_0 + \singexpalg{\tau-1+\gamma}(\Omega) \]
of the space $\singexpalg{\tau-1}(\Omega)$ defined in Section~\ref{fn-spaces}. Here, $f_0$ is the prototype solution \eqref{eqn:test_solution} from Theorems \ref{thm:basic_volterra}--\ref{thm:proto-growth}, which belongs to the space $\singexpalg{\tau-1}(\domain)$.
\end{theorem}
\begin{rev}\begin{corollary}\label{cor:expand_uniq}
Under the conditions of Theorem~\ref{thm:general_volterra}, for any $\rho > \tau$, the equation $f = \volterra f$ has at most one solution in $f_0 + \singexpalg{\rho-1}(\Omega)$. 
\end{corollary}\end{rev}
This result will follow from a more general result about inhomogeneous equations.
\begin{lemma}\label{lem:perturbed_volterra}
Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}. Suppose we are also given a function $g$, which for some $\rho > \tau$ belongs to the space $\singexpalg{\rho-1}(\Omega)$ defined in Section~\ref{fn-spaces}. Then the inhomogeneous equation
\[ f = \volterra f + g, \]
has a unique solution $f$ in the space $\singexpalg{\rho-1}(\Omega)$.
\end{lemma}
We will prove Lemma~\ref{lem:perturbed_volterra} in Sections \ref{sec:V is a contraction}--\ref{sec:existence and uniqueness}, using the contraction mapping theorem. The heart of the argument is Proposition~\ref{prop:get-contraction}, which shows us how to find relevant subspaces where $\volterra$ is a contraction.

@@

\begin{oldnot}
\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_{\zeta = 0}^a |k(a,\cdot)\,\varphi\;d\zeta| \]
\end{oldnot}
\begin{newnot}
\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_{\zeta(a') = 0}^a |k(a, a')\,\varphi(a')\;d\zeta(a')| \]
\end{newnot}

@@

\begin{oldnot}

@@

|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_{\zeta = 0}^a |k(a,\cdot)|\,|\zeta|^{\rho-1}\,e^{\Lambda |\zeta|}\,\|\varphi\|_{\rho-1, \Lambda}\;|d\zeta| \\
& = \|\varphi\|_{\rho-1, \Lambda}  \int_{\zeta = 0}^a |k(a, \cdot)|\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|

@@

\end{oldnot}
\begin{newnot}
|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_{\zeta(a') = 0}^a |k(a, a')|\,|\zeta(a')|^{\rho-1}\,e^{\Lambda |\zeta(a')|}\,\|\varphi\|_{\rho-1, \Lambda}\;|d\zeta(a')| \\
& = \|\varphi\|_{\rho-1, \Lambda}  \int_{\zeta(a') = 0}^a |k(a, a')|\,\left|\frac{\zeta(a')}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta(a')|)}\;|d\zeta(a')|
\end{newnot}

@@

\|\varphi\|_{\rho-1, \Lambda}  \int_{\zeta = 0}^a \frac{\sigma}{|\zeta(a)|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta| \\
& \le \sigma \|\varphi\|_{\rho-1, \Lambda}  \int_{\zeta = 0}^a \left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;\left|\frac{d\zeta}{\zeta(a)}\right|
